---
title: "HW 5"
author: "Jaclyn Verity - jv2629"
date: "November 6, 2018"
output: github_document
---
Setup for success!
```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

## Problem 1

**Reading in the data and making it workable.**
```{r}
file_base_con = "./data/con_0"

file_base_exp = "./data/exp_0"

vec_con = str_c(file_base_con, 01:10) %>% str_c(".csv")

vec_exp = str_c(file_base_exp, 01:10) %>% str_c(".csv")

read_cases = function(file_name) {
  read_csv(file_name)
}

list_con = map(vec_con, read_cases)

list_exp = map(vec_exp, read_cases)

tbl_con = tibble(list_con) %>% unnest()

tbl_exp = tibble(list_exp) %>% unnest()
```

**Cleaning up and combining the data.**
```{r}
tbl_con = tbl_con %>% 
  mutate(subject_id = row_number(), 
         as.character(subject_id), 
          subject_id = str_c(subject_id, "c"),
         group = "control")

tbl_exp = tbl_exp %>% 
  mutate(subject_id = row_number(), 
         as.character(subject_id),
        subject_id = str_c(subject_id, "e"),
         group = "experimental")
 

all_cases = bind_rows(tbl_exp, tbl_con)
```

**Spaghetti plot.**
```{r}

df_case_ploting = all_cases %>% 
  group_by(group, subject_id) %>% 
  gather(key = time, value = value, week_1:week_8)

ggplot(df_case_ploting, aes(x = time, y = value, group = subject_id, color = group)) +
  geom_line()

```

At week 1 the control and experimental subjects had a mix of values with no clear distinction between the two groups. Over time the experimental subjects all increased in values while controls stayed about the same. The final values recorded at 8 weeks show a clear segregation between the groups. The experimental groups all have values about 2.5 while the controls all have values below 2.5. 

#Problem 2

**Load and describe the homicide data set.**
```{r}

require(RCurl)

hom_raw = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 
```

The raw homicide data has 52,179 homicides and 12 variables. It includes a unique id for each homicide, with the code linked to the city where the homicide happened and then a number in order of report date. Other variables include the date the homicide was reported, the victims first and last name, race, age, and sex. Geographic information on where the homicide occured include city, state, and coordinates. Finally there is the disposition column which informs on whether an arrest was made on the homicide. 

**Create new variables and tidy the data set.**
```{r}
hom_total = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', ')) %>% 
  group_by(city_state) %>% 
  summarise(total_homicide = n())

hom_unsolved = hom_raw %>% 
  mutate(city_state = paste(city, state, sep = ', ')) %>% 
  group_by(city_state) %>% 
  filter(str_detect(disposition, "without|Open")) %>%
  summarise(unsolved_homicide = n())

hom_sum = full_join(hom_total, hom_unsolved)
```

**Find the proportion of unsolved murders in Baltimore, MD.**
```{r}

unsolved_balt = hom_sum %>% 
  filter(str_detect(city_state, "Baltimore, MD")) %>% 
  pull(unsolved_homicide)

total_balt = hom_sum %>% 
  filter(str_detect(city_state, "Baltimore, MD")) %>% 
  pull(total_homicide)

ouput_balt = prop.test(unsolved_balt, total_balt)

broom::tidy(ouput_balt)
```


